Machine Learning rooted Potential piloted RRT* for expeditious Path Planning

### 2019-02-27 Research Paper/paper.tex
paper parallel

Now how much the tree should grow towards the destination relative to growing away from the obstacles, dependant on $k$ and $k^\prime$ is a very sensitive parameter and has serious implications(Fig 2 and Fig 3).
\vspace{3mm}
\begin{figure}
\begin{center}
\includegraphics[scale=1.5]{tree.png}
    \caption{ The tree growth of RRT-Star with APF for a non-ideal value of Potential Function. It is evident that repulsion from the obstacle is not significant enough and that there is unnecessary branching of the tree. The final path is not a good approximation of the shortest path.(Fig 4)} \label{fig1}
\end{center}
\end{figure}
\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{stuckyy.png}
    \caption{ An illustration of a case where the tree gets stuck in a local minimum, due to highly unsuitable value of Potential Function.}\label{fig1}
\end{center}
\end{figure}

@@

\subsection{Ideal Path and Potential Constants:}
To find the ideal constants of potential field , we first found the ideal path by using BFS and Dijkstra. These ideal paths were then made use of in the neural networks later on. An example is shown in the figure above (Fig 5).

\subsection{Training:}
The position of the obstacle is an important determinant of the RRT* Tree. So is the area of the obstacle. So we took the centres of the each obstacle blob and the total area of the obstacles as the features of the neural network. We designed the cost function by comparing the predicted path after an epoch and the ideal path. Using this we predicted the potential function. We then used the potential function thus predicted to run an RRT* APF tree and an example is shown in Fig. 3.
\vspace{10mm}
\begin{figure}
\begin{center}
\includegraphics[scale=1.5]{img_bam.png}
    \caption{ The tree growth and piloted sampling of the nodes in RRT-Star with APF for the trained value of Potential Function. The tree converges directly to the destination and provides a very good approximation of the shortest path.} \label{fig1}
\end{center}
\end{figure}

\section{\centering{Comaparison}}
\subsection{Time of convergence:}
\subsection{Width of the tree:}
% \begin{figure}
% We conducted an experiment based on tree generation time given a set of obstacles. The experimental setup included ROS based communication nodes and a GUI based interactive platform for setting up the environment. This was performed on Linux 4.4.0-127-generic with 8 GiB memory and 2.3 GHz x 8 CPU.
% % \vspace{-1mm}
% \begin{table}[]
% \centering
% \caption{Comparison of time (in milli seconds) in generation of path}
% \label{Comparison with other planners}
% \begin{tabular}{@{}c|@{\hskip 0.1in}cccl@{}}
% \toprule
% \multirow{\textbf{Obstacles}} & \multicolumn{4}{c}{\textbf{Average Traversal Time}}              
% \\
%  & \textbf{PGD-RRT*} & \textbf{RRT*} & \textbf{RT-RRT*} & \textbf{Our planner} \\
%  \hline
% 5 & 4.1996  &  3.7078  &  3.7951  & 2.7958\\
% 7 & 4.2315  &  3.7912  &  3.8105  & 2.8110\\
% 9 & 4.2555  &  3.9105  &  3.8492  & 2.8862\\
% 10 & 4.2658 &  3.9824  &  3.8908  & 2.8873\\
% 12 & 4.3655 &  4.1473  &  4.1335  & 3.1080\\
% 15 & 4.4662 &  4.2194  &  4.3264  & 3.1866\\
% 18 & 4.6905 &  4.4505  &  4.5155  & 3.4242\\
% 20 & 4.9696 &  4.9191  &  4.9583  & 3.9823\\ 
% \end{tabular}
% \vspace{-6mm}
% \end{table}
% Thus, it can be seen that our planner takes nearly the same time to generate the tree given similar set of environmental conditions. Along with that, our planner provides a more optimised path. The average number of iterations required to find the path to each goal was 10.36 for our method and 18.43 for RT-RRT*.\\
% \vspace{-6mm}
% \subsubsection{Replanning}
% In a dynamic environment, the replanning of path is an important aspect. Moving obstacles when come along the path, a new path has to be found incorporating the new position of the obstacles. For better performance of agents, this replanning of path should take place in less amount of time. Our proposed path planner outperforms other planners in this, hence making it suitable for a real-time dynamic environment. With respect to the PGD-RRT*, our path planner is very quick in replanning as the tree growth does not take place again and again, but gets rewired when required. With respect to the RT-RRT*, our planner provides a more optimised path, which is clear from the illustration provided (fig 3) and Table 1. Our planner is based on a dynamic environment only and can be outperformed by other planners in a static environment.

>>>>

Now how much the tree should grow towards the destination relative to growing away from the obstacles, dependant on $k$ and $k^\prime$ is a very sensitive parameter and has serious implications(Fig 2 and Fig 3).
\vspace{3mm}

@@

\subsection{Ideal Path Data Genration:}
To find the ideal constants of potential field , we first found the ideal path by using BFS and Dijkstra. This ideal paths took a considerable amount of time to form, but this a one-time investment for training. Once, the ideal path for all the 1,00,000 is generated is stored in the form of a list of coordinates for further use. These ideal paths were then made use of in the neural networks. An example is shown in the figure below (Fig 3).
 \vspace{5mm}

\subsection{Training:}
The position of the obstacle is an important determinant of the RRT* Tree. So is the area of the obstacle. So we took the centres of the each obstacle blob and the total area of the obstacles as the features of the neural network. We designed the cost function by comparing the predicted path after an epoch and the ideal path by comparing the path coordinate lists using mean square error. With this custom error function we built a neural network with the help of Keras. We had two hidden layers. We used 5 fold cross validation to improve the neural network. We also made use Adam's optimizer. Using this we predicted the potential function. We then used the potential function thus predicted to run an RRT* APF tree and an example is shown in Fig. 3.
\vspace{10mm}
\begin{figure}
\begin{center}
\includegraphics[scale=1.5]{img_bam.png}
    \caption{ The tree growth and piloted sampling of the nodes in RRT-Star with APF for the trained value of Potential Function. The tree converges directly to the destination and provides a very good approximation of the shortest path.} \label{fig1}
\end{center}
\end{figure}

\section{\centering{Results and Improvements:}}
\subsection{Time of convergence:}
The RRT* tree with the predicted values of potential functions converged faster than normal RRT* tree. For non ideal potential values, normal RRT* tree would get stuck at local minima which was being avoided by the predicted values.

The following table show the comparison between RRT* tree and the RRT* APF tree with predicted potential functions, wrt. to the time of covergence.

\vspace{10mm}
\begin{center}
\begin{tabular}{ |p{1cm}||p{3cm}|p{3cm}|  }
 \hline
 \multicolumn{3}{|c|}{Time of Convergence} \\
 \hline
 S.No. & RRT* &DL RRT* APF\\
 \hline
 1   & AF    &AFG\\
 2&   AX  & ALA   \\
 3 &AL & ALB\\
 4    &DZ & DZA\\
 5&   AS & WWR \\
6& AD  & AND\\
 7& AO  & AGO\\
 8& AO  & AGO\\
 9& AO  & AGO\\
 10& AO  & AGO\\
 \hline
\end{tabular}
\end{center}

\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{stuckyy.png}
    \caption{ An illustration of a case where the tree gets stuck in a local minimum, due to highly unsuitable value of Potential Function, which is avoided using learning techniques}\label{fig1}
\end{center}
\end{figure}

\subsection{Width of the tree:}
The width of the tree also reduced significantly implying that the predicted values of potential functions were close to the ideal ones. The images below show the comparison between RRT* and DL RRT* APF with respect to the width of the tree.

\begin{figure}
\begin{center}
\includegraphics[scale=1.5]{tree.png}
    \caption{ The tree growth of RRT-Star with APF for a non-ideal value of Potential Function. It is evident that repulsion from the obstacle is not significant enough and that there is unnecessary branching of the tree. The final path is not a good approximation of the shortest path.(Fig 4)} \label{fig1}
\end{center}
\end{figure}
% \begin{figure}
% We conducted an experiment based on tree generation time given a set of obstacles. The experimental setup included ROS based communication nodes and a GUI based interactive platform for setting up the environment. This was performed on Linux 4.4.0-127-generic with 8 GiB memory and 2.3 GHz x 8 CPU.
% % \vspace{-1mm}
% \begin{table}[]
% \centering
% \caption{Comparison of time (in milli seconds) in generation of path}
% \label{Comparison with other planners}
% \begin{tabular}{@{}c|@{\hskip 0.1in}cccl@{}}
% \toprule
% \multirow{\textbf{Obstacles}} & \multicolumn{4}{c}{\textbf{Average Traversal Time}}              
% \\
%  & \textbf{PGD-RRT*} & \textbf{RRT*} & \textbf{RT-RRT*} & \textbf{Our planner} \\
%  \hline
% 5 & 4.1996  &  3.7078  &  3.7951  & 2.7958\\
% 7 & 4.2315  &  3.7912  &  3.8105  & 2.8110\\
% 9 & 4.2555  &  3.9105  &  3.8492  & 2.8862\\
% 10 & 4.2658 &  3.9824  &  3.8908  & 2.8873\\
% 12 & 4.3655 &  4.1473  &  4.1335  & 3.1080\\
% 15 & 4.4662 &  4.2194  &  4.3264  & 3.1866\\
% 18 & 4.6905 &  4.4505  &  4.5155  & 3.4242\\
% 20 & 4.9696 &  4.9191  &  4.9583  & 3.9823\\ 
% \end{tabular}
% \vspace{-6mm}
% \end{table}
% Thus, it can be seen that our planner takes nearly the same time to generate the tree given similar set of environmental conditions. Along with that, our planner provides a more optimised path. The average number of iterations required to find the path to each goal was 10.36 for our method and 18.43 for RT-RRT*.\\
% \vspace{-6mm}
% \subsubsection{Replanning}
% In a dynamic environment, the replanning of path is an important aspect. Moving obstacles when come along the path, a new path has to be found incorporating the new position of the obstacles. For better performance of agents, this replanning of path should take place in less amount of time. Our proposed path planner outperforms other planners in this, hence making it suitable for a real-time dynamic environment. With respect to the PGD-RRT*, our path planner is very quick in replanning as the tree growth does not take place again and again, but gets rewired when required. With respect to the RT-RRT*, our planner provides a more optimised path, which is clear from the illustration provided (fig 3) and Table 1. Our planner is based on a dynamic environment only and can be outperformed by other planners in a static environment.
